---
title: "R_FinalProject"
format:
  html:
    theme: yeti
editor: visual
echo: false
---


```{r}
library(here)
library(readr)
library(dplyr)
library(gtsummary)
library(ggplot2)

orders <- read_csv(here((here::here("/Users/suzain/Downloads/Food.csv"))))
```
This analysis used data from Kaggle on Food Panda orders in Pakistan, containing `r nrow(orders)` rows and `r ncol(orders)` columns. The dataset includes information on customer demographics, order details, and transaction characteristics. The source is an open-access Kaggle dataset: Foodpanda Analysis Dataset 2025.

```{r}
#| label: tbl-characteristics
#| tbl-cap : "Customer Characteristics" 
tbl_summary(
	orders,
	by = gender,
	include = c(city, restaurant_name, dish_name, category, payment_method, delivery_status ),
	label = list(
	city ~ "City",
	restaurant_name ~ "Restaurant Name",
	dish_name ~ "Name of the Dish",
	category ~ "Category",
	payment_method ~ "Payment Method",
	delivery_status ~ "Delivery Status"
	)
) |>
	add_p(test = list(
		all_continuous() ~ "t.test", 
		all_categorical() ~ "chisq.test"
)) |>
	bold_labels() |>
  add_overall(col_label = "**Total**")

stats <- list(n = nrow(orders),
							mean_orderfrequency = mean(orders$order_frequency))



```
There were `r stats$n` users with a mean order frequency of `r stats$mean_orderfrequency`



```{r}

```


```{r}

```

